My title

### 2023-03-15 outputs/paper/paper.qmd
Added table that shows a subset of the key features of our dataset.
Adding headers to Quarto paper

# Introduction

@@

# Data {#sec-data}

@@

## Survey

## Questionnaire

# Results

@@

# Discussion {#sec-discussion}

## First discussion point {#sec-first-point}

## Second discussion point {#sec-second-point}

## Third discussion point {#sec-third-point}

## Weaknesses and next steps {#sec-weaknesses}

## Ethics and Bias {#sec-bias}

@@

# Appendix {.unnumbered}

# Additional details

# References

>>>>

# 1 Introduction

@@

# 2 Data {#sec-data}

## 2.1 Overview of Data

### 2.1.1 Data Source

### 2.1.2 Variables of Interest

@@

## 2.2 Survey

## 2.3 Questionnaire

# 3 Results

@@

# 4 Discussion {#sec-discussion}

## 4.1 First discussion point {#sec-first-point}

## 4.2 Second discussion point {#sec-second-point}

## 4.3 Third discussion point {#sec-third-point}

## 4.4 Weaknesses and next steps {#sec-weaknesses}

## 4.5 Ethics and Bias {#sec-bias}

@@

# 5 Appendix {.unnumbered}

# 6 Additional details

# 7 References
